Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

The functions $F_1,F_2,F_3,...$ now have meaningful names such as relu\_1, conv\_2 now.
[Not actually necessary to know but insert your elaborations here]

@@

The vanillay neural style transfer algorithm \cite{nst} is 
structured as iteratively solving an optimisation problem.
The argument to optimise is the image as a multidimensional array,
of size $1\times3\times512\times512$ for example.
The interative solver can be many, but in our case it is 
L-BFGS [Maybe elaborate on L-BFGS here]. 
The initial value of the argument could be either white noise or the content image,
but the latter appeared to make the optimisation much easier.

@@

The content loss is the easier one to explain of the two losses.
It is the mean square error between the outputs of a certain function in the
vgg19 taking the current argument image and the content image as inputs respectively.
We say ``a certain'' function because the output of which function to choose is
adjustable.
A typical choice is the output of \verb|conv_4| function. See Figure \ref{contentloss}.
\begin{figure}
\center
\includegraphics[width=\textwidth]{contentloss.pdf}
\caption{The content loss \label{contentloss}}
\end{figure}

\subsection{Data Set}

\subsubsection {Format and Preparation}

\subsubsection {(Not Really) Time-Series}

\subsubsection {Rationale}

\subsection{Hyperparameters and Experiments}

For the vanilla style-transfer algorithm, there were a few hyper-parameters that 
affected the result.
\begin{itemize}
\item Number of iterations in the optimization. 
We did not have to expriment with different numbers of iterations though.
It was more sensible to run the algorithm for more-than-enough iterations and store the intermediate results.
\item Choice of initial values. Some sensible choices were:
\begin{itemize}
\item White noise.
\item White.
\item Black.
\item The model mean.
\item The content image.
\item The style image.
\item The average of the content image and the style image.
\end{itemize}
\end{itemize}

%\subsubsection{Activation Function}

\subsubsection{Learning Rate}

\subsubsection{Hidden Layer Size}

\subsection{Evaluating Prediction}

\subsubsection{Binarisation and Choice of Loss}

\subsubsection{Amount of Network Reduction}

\subsubsection{Mechanism}

\subsubsection{Execution}

The program was developed under and are compatible with:
\begin{itemize}
\item Python 3.6
\item PyTorch 1.0.1.post2
\item CentOS 7 x86\_64
\end{itemize}
To run the code, execute shell commands like
\begin{verbatim}
python36 0.py 5000
\end{verbatim}
where 5000 is the number of desired training cycles to reach.
The different hyperparameters will be automatically covered.
The program automatically picks up stored models.
To start fresh, clear the stored models and outputs by
\begin{verbatim}
rm out/*/*.*
\end{verbatim}
but do not remove the directories.

\section{Results and Discussion}

>>>>

The functions $F_1,F_2,F_3,...$ now have meaningful names such as relu\_1, conv\_2 now.
[[[[Not actually necessary to know but insert your elaborations here]]]]

@@

The vanillay neural style transfer algorithm \cite{nst} is 
structured as iteratively solving an optimisation problem.
The argument to optimise is the image as a multidimensional array,
of size $1\times3\times512\times512$ for example.
The interative solver can be many, but in our case it is 
L-BFGS [[[[Maybe elaborate on L-BFGS here]]]]. 
The initial value of the argument could be either white noise or the content image,
but the latter appeared to make the optimisation much easier.

@@

The content loss $L_\text{content}$ is the easier one to explain of the two losses.
It is the mean square error between the outputs of a certain function in the
vgg19 taking the current argument image and the content image as inputs respectively.
We say ``a certain'' function because the output of which function to choose is
adjustable.
A typical choice is the output of \verb|conv_4| function. See Figure \ref{contentloss}.
\begin{figure}
\center
\includegraphics[width=\textwidth]{contentloss.pdf}
\caption{The content loss $L_{content}$ \label{contentloss}}
\end{figure}

The style loss $L_\text{content}$ can actually be a sum of several style losses, or sometimes just one.
For each style loss, 
both the current image under optimisation and the style image are passed through the vgg19 model.
The two outputs of a certain function in the model are extracted, 
and converted to Gram matrices. We will elabrate on what Gram matrices are,
for now they are just square matrices computed from multidimensional arrays (i.e. feature maps).
For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array
is a $64\times64$ matrix.
The point is to compute something that describe the distributions of features
in the image without the spatial information of where the features are.
Gram matrices describe the distributions with correlation between features.
The several style losses are computed with the outputs of different functions.
Otherwise, each of the several style losses are computed in exactly the same way.

Again outputs of which functions in the model to derive style losses from is really adjustable.
A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
the style losses derived \verb|conv_1| and \verb|conv_4| in Figure $\ref{stylelosses}$.

\begin{figure}
\center
\includegraphics[width=\textwidth]{stylelosses}
\end{figure}

\subsection{Gram matrix}
[[[[Elaborate on gram matrix here]]]]

\subsection{Removing the spatial information in other ways}
We think that the most brilliant aspect of the neural style transfer algorithm,
apart from the general structure, is the use of Gram matrices to compare 
distributions of features in two images, so that where the features are does not matter.
It gives really nice insight on what ``artistic style'' means.

However, could we achieve the same results with other

\section{Experiments and Discussion}
